---
title: "Brownlows Bets"
author: "Put your name here!"
date: "put the date here"
output: html_document: default
 ---

<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

 At the first day of class there are 35 students in Math Statistics class and professor Brownlow always proposes this bet to his students "I will wager $2 to your bet of $1 that at least two people in today's class have  the same birthday.  He tells me he has made that bet 1137 times so far. Where do you think his profits are? Discuss this in a markdown document

# Methods

<!--Decide on your methods:  In this section explain the approach you will take to attack the issue --- how will you decide on a likely estimate of professor Brownlow's earnings or losses after 1137 bets. Also explain how you construct a 95% confidence interval about your estimate of his winnings !-->

we will approach this problem through a sequence of simulations.  First we will let the numbers going from 1 to 365 represent the different possible Bdays a student could have(1 would be Jan 1st, 32 would be Feb 1st etc). Then we will randomly select(with replacement to insure two of the same number could be chosen)35 numbers to represent the class. Then we need to examin the numbers chosen to see if any are duplicates (a duplicate would represent two people with the same Bday). If there is a duplicate we will give Brownlow 1 dollar for this bet, if not we will take 2 dollars away from him. We will do this same procedure 1137 times. at the end we will total his winnings and loosings and we will use that number as an estimate of his take-home.
#Profit Estimate

<!--Explain and display the results of your method of coming up with the estimate of professor Brownlows betting!-->

First we create our Bdays

```{r}
Bdays <- 1:365
brownprofit=numeric(1137)
timesdone=numeric(30)
```
now we pick 35 of them to form a class and loop thru 1137 classes keeping score.
```{r}
for (i in 1:1137) {

ourclass <- sample (x=Bdays,size=35, replace= TRUE)

xx <- anyDuplicated(ourclass)

#now we need to see if any two in our class match

brownprofit[i]<- ifelse(xx>0,1,-2)
}

hiswinning <- sum(brownprofit)
print (hiswinning)

```
### Brownlows profit `r hiswinning`



# Confidence interval of Brownlows earning

<!--Explain and display your method of coming up with a 95% confidence interval of  professor Brownlows-->

```{r}
Bdays <- 1:365
brownprofit=numeric(1137)
timesdone=numeric(30)
```
now we pick 35 of them to form a class and loop thru 1137 classes keeping score.
```{r}
for (j in 1:30){
for (i in 1:1137) {

ourclass <- sample (x=Bdays,size=35, replace= TRUE)

xx <- anyDuplicated(ourclass)

#now we need to see if any two in our class match

brownprofit[i]<- ifelse(xx>0,1,-2)
}

hiswinning <- sum(brownprofit)
timesdone[j] <- hiswinning
}
```

# Discussion and Conclusion

<!--Discussion and conclusion here.  If professor Brownlow is consistantly making or losing money how could he change his payout so that his profits center on zero?  Also discuss what size his class should be in order to have his current scheme balance at zero profit.!-->

